Magnetized accretion disks around Kerr black holes with scalar hair - I. Constant angular momentum disks

### 2018-11-19 paper_prd.tex
More work.

In recent years, new families of stationary, asymptotically flat black holes (BHs) avoiding the so-called ``no hair" theorems, have been obtained both in general relativity and modified gravity (see e.g.~\cite{Herdeiro:2015_review} and references therein). Among those, Kerr BHs with synchronised hair~\cite{Herdeiro:2014a,Herdeiro:2016} are a counterexample to the no hair conjecture resulting from minimally coupling Einstein's gravity to simple (bosonic) matter fields obeying all energy conditions. The physical conditions and stability properties of these classes of {\it hairy} BHs  (HBHs) have been recently investigated to assess their potential viability as  alternatives to astrophysical Kerr BHs.  On the one hand, Kerr BHs with Proca hair have been shown to form dynamically as the end-product of the superradiant instability~\cite{East:2017,Herdeiro:2017} (see also~\cite{Sanchis-Gual:2016,Bosch:2016} for the case of a charged scalar field around a charged BH in spherical  symmetry). On the other hand, the stability of these solutions, questioned by~\cite{Ganchev:2018} in the scalar case, has been recently revisited by~\cite{Degollado:2018} who have shown that the domain of HBH solutions for which the superradiant instability might affect their actual existence has no significance for astrophysical BHs, rendering HBHs as {\it effectively} stable.

@@

The setup considered by~\cite{Vincent:2016} in which the light source producing the BH shadow is an accretion disk, is arguably more realistic than the distant celestial sphere of~\cite{Cunha:2015}. Thick accretion disks (or tori) are common systems in astrophysics, either surrounding the supermassive central BHs of quasars and active galactic nuclei or, at  stellar scale, surrounding the compact objects in X-ray binaries, microquasars, and gamma-ray bursts (see~\cite{Abramowicz:2013} and references therein). In this paper we present new families of stationary solutions of magnetized thick accretion disks around KBHsSH that differ from those considered by~\cite{Vincent:2016}. Our procedure, which combines earlier approaches put forward by~\cite{Komissarov:2006,Qian:2009} was presented in~\cite{Gimeno-Soler:2017} for the Kerr BH case. In Ref.~\cite{Gimeno-Soler:2017} we built equilibrium sequences of accretion disks  in the test-fluid approximation endowed with a purely toroidal magnetic field, assuming a form of the angular momentum distribution that departs from the constant case considered by~\cite{Komissarov:2006} and from which the location and morphology of the equipotential surfaces can be numerically computed. Our goal in the present work is to extend this approach to KBHsSH and to assess the dependence of the morphology and properties of accretion disks on the type of BH considered, either Kerr BHs of varying spins or KBHsSH. In this investigation we focus on disks with a constant distribution of specific angular momentum. In the  purely hydrodynamical case, such a model is commonly refereed to as a `Polish doughnut', after the seminal work by~\cite{Abramowicz:1978} (but see also~\cite{Fishbone:1976}). In a companion paper we will present the non-constant (power-law) case, whose sequences have already been computed. The dynamical (non-linear) stability of these solutions as well as the analysis of the corresponding shadows will be discussed elsewhere.

The organization of this paper is as follows: Section~\ref{framework} presents  the mathematical framework we employ to build magnetized disks in the numerically generated spacetimes of KBHsSH. Section~\ref{procedure} discusses the corresponding numerical methodology to build the disks. Sequences of equilibrium models are presented in Section~\ref{results} along with the discussion of their morphological features and properties. Finally, our conclusions  are  summarized  in  Section~\ref{conclusions}. Geometrized units ($G=c=1$) are used throughout.

@@

The approach we followed in~\cite{Gimeno-Soler:2017} for the angular momentum distribution of the disks was introduced by~\cite{Qian:2009}, and it is characterized by three free parameters, $\beta$, $\gamma$, and $\eta$ (see Eq.~(7) in~\cite{Gimeno-Soler:2017}). In this work, for simplicity and to reduce the ample space of parameters of the system, we consider a constant angular momentum distribution, $l(r,\theta) = \mathrm{const}$, which corresponds to setting $\beta=\gamma=0$ in~\cite{Gimeno-Soler:2017}. This choice also allows for the presence of a cusp (and hence matter accretion onto the black hole) and a centre. Following~\citep{Daigne:2004}, the specific value of the angular momentum corresponding to bound fluid elements ($-u_t<1$) is computed as the minimum of the following equation
\begin{equation}\label{eq:mb_ang_mom}
l^{\pm}_{\mathrm{b}}(r, \theta) = \frac{g_{t\phi} \pm \sqrt{ (g_{t\phi}^2-g_{tt}g_{\phi\phi})  (1+g_{tt}) } }{-g_{tt}}\,,
\end{equation}
where the plus sign corresponds to prograde orbits and the minus sign to retrograde orbits. Our convention is that the angular momentum of the BH is positive and the matter of the disk rotates in the positive (negative) direction of $\phi$ for a prograde (retrograde) disk.
Equation~(\ref{eq:mb_ang_mom}) is given by~\citep{Daigne:2004} for Kerr BHs, but it is valid for any stationary and axisymmetric spacetime. For prograde motion, the function has a minimum outside the event horizon. The location of this minimum corresponds with the marginally bound orbit $r_{\mathrm{mb}}$, and the angular momentum corresponds to the Keplerian angular momentum $l_{\mathrm{mb}}$ at that point. We show the proof of this statement in Appendix~\ref{ang_mom_appendix}.

@@

To account for the magnetic field in the disks we use the procedure described by~\cite{Komissarov:2006,Montero:2007}. First, we write the equations of ideal general relativistic MHD as the following conservation laws, $\nabla_{\mu} T^{\mu\nu} = 0$, $\nabla_{\mu} \,^\ast F^{\mu\nu} = 0$, and 
$\nabla_{\mu} (\rho u^{\mu}) = 0$, 
where $\nabla_{\mu}$ is the covariant derivative and
\begin{equation}\label{eq:e-m_tensor}
T^{\mu\nu} = (\rho h + b^2)u^{\mu}u^{\nu} + (p + p_{\mathrm{m}})g^{\mu\nu} - b^{\mu}b^{\nu},
\end{equation}
is the energy-momentum tensor of a magnetized perfect fluid, $h$, $\rho$, $p$, and $p_{\mathrm{m}}$ being the fluid specific enthalpy, density, fluid pressure, and magnetic pressure, respectively, the latter defined as $p_{\mathrm{m}} = b^2/2$. The ratio of fluid pressure to magnetic pressure defines the magnetization parameter $\beta_{\mathrm{m}} = p/p_{\mathrm{m}}$.
Moreover, $^\ast F^{\mu\nu} = b^{\mu}u^{\nu} - b^{\nu}u^{\mu}$ is the (dual of the) Faraday tensor relative to an observer with 
four-velocity $u^{\mu}$, and $b^{\mu}$ is the magnetic field in that frame, with
$b^2=b^{\mu}b_{\mu}$ (see~\cite{Anton:2006} for further details). Assuming the magnetic field is purely azimuthal, i.e.~$b^r = b^{\theta} = 0$,
and taking into account that the flow is stationary and axisymmetric, the conservation of the current density and of the Faraday tensor follow. Contracting the divergence of Eq.~\eqref{eq:e-m_tensor} with the projection tensor $h^{\alpha}_{\,\,\beta} = \delta^{\alpha}_{\,\,\beta} + u^{\alpha}u_{\beta}$, we arrive at
\begin{equation}
(\rho h + b^2)u_{\nu}\partial_i u^{\nu} + \partial_i\left(p + \frac{b^2}{2}\right) - b_{\nu}\partial_i b^{\nu}=0\,,
\end{equation}
where $i = r, \theta$. This equation can be rewritten in terms of the specific angular momentum $l$ and of the angular velocity $\Omega$, 
\begin{equation}\label{eq:diff_ver}
\partial_i(\ln |u_t|) - \frac{\Omega \partial_i l}{1-l\Omega} + \frac{\partial_i p}{\rho h} + \frac{\partial_i(\mathcal{L}b^2)}{2\mathcal{L}\rho h} = 0\,,
\end{equation}
where $\mathcal{L} = g_{t\phi}^2 - g_{tt}g_{\phi\phi}$.

@@

\begin{figure*}
\centering
\includegraphics[scale=0.37]{figures/radial_log_rho_model_I.pdf}
\hspace{-0.6cm}
\includegraphics[scale=0.37]{figures/radial_log_rho_model_IV.pdf}
\hspace{-0.6cm}
\includegraphics[scale=0.37]{figures/radial_log_rho_model_VII.pdf}
\hspace{-0.6cm}
\\
\hspace{-0.6cm}
\includegraphics[scale=0.37]{figures/log_radial_log_rho_I_ADM.pdf}
\hspace{-0.6cm}
\includegraphics[scale=0.37]{figures/log_radial_log_rho_IV_ADM.pdf}
\hspace{-0.6cm}
\includegraphics[scale=0.37]{figures/log_radial_log_rho_VII_ADM.pdf}
\hspace{-0.6cm}
\caption{Size of the disks. Top panel: Effects of the magnetization on the radial profiles of the logarithm of the density at the equatorial plane for different KBHsSH models. From left to right we show model I, IV, and VII, respectively. Bottom panel: same as the top panel but for Kerr BHs. From left to right the cases shown have the same ADM quantities as the KBHsSH model I, IV, and VII, respectively, shown in the top panel.}
\label{radial_profiles_HBH}
\end{figure*}

@@

Before building the models, it is important to note that we need a sufficiently fine numerical grid to fully capture the behaviour of the physical magnitudes at the innermost regions of the disk. For this reason, we use a non-uniform $(r, \theta)$ grid with a typical domain given by $[r_{\mathrm{H}}, 199.2] \times [0, \pi/2]$ and a typical number of points $N_r \times N_{\theta} = 2500 \times 300$. Those numbers are only representative as the actual numbers depend on the horizon radius $r_{\mathrm{H}}$ and on the specific model. The spacetime metric data on this grid is interpolated from the original data obtained by~\cite{Herdeiro:2015b}. The original grid in~\cite{Herdeiro:2015b} is a uniform ($x$, $\theta$) grid (where $x$ is a compactified radial coordinate) with a domain $[0, 1] \times [0, \pi/2]$ and a number of points of $N_x \times N_{\theta} = 251 \times 30$~\footnote{Some samples are presented in~\cite{grav_web}}. To obtain our grid, we use the coordinate transformation provided in~\cite{grav_web} and interpolate the initial grid using cubic splines interpolation. An example of our grid is shown in Fig.~XXX. \tf{We will include this figure if it could be done and were meaningful.} \tf{Maybe we could also provide the number of the domain and number of points we need for our most extreme case with $a = 0.9999$.}

\sg{It may be important to note that it seems that we have not angular resolution enough to resolve the morphology of the disk in these extreme cases (see the 2D perimeteral plots). But I think this should go in the results section.} \tf{I agree with mentioning this in the results section.} \sg{Added.}

@@

We start presenting the morphological distribution of the models in the ($r\sin\theta, r\cos\theta$) plane in figures~\ref{models_I} and~\ref{models_II}. The radial coordinate employed in these figures is the standard one of the spherical coordinate system. Figures~\ref{models_I} and~\ref{models_II} show the rest-mass density distribution for all our KBHsSH models for 3 different values of the magnetization parameter at the centre of the disks, $\beta_{\mathrm{m_c}}$, namely $10^{10}$ (unmagnetized, left column), $1$ (mildly magnetized, middle column) and $10^{-10}$ (strongly magnetized, right column).

@@

\begin{table*}[t]
\caption{Disk parameters and values of their relevant physical magnitudes for the Kerr BH case. For all models, $R_{\mathrm{in}} = R_{\mathrm{mb}}$ , $l = l_{\mathrm{mb}}$ and $M_{\mathrm{BH}} = 1$. \tf{Complete description.}}        
\label{KBH_disk_parameters}      
\centering          
\begin{tabular}{c c c c c c  c c c c c c c}
\hline\hline       
 $a$ & $\mathfrak{s}$ &  $l$ & $W_{\mathrm{c}}$ & $R_{\mathrm{in}}$ & $R_{\mathrm{c}}$ &  $\beta_{\mathrm{m_{\mathrm{c}}}}$ & $h_{\mathrm{max}}$ & $\rho_{\mathrm{max}}$ & $p_{\mathrm{max}}$ & $p_{\mathrm{m, max}}$ & $R_{\mathrm{max}}$ & $R_{\mathrm{m, max}}$\\ 
\hline           
$0$ & $1$ & $4.00$ & $-4.32 \times 10^{-2}$ & $4.00$ & $10.47$ & $10^{10}$ & $1.04$ & $1.00$ & $1.10 \times 10^{-2}$ & $1.15 \times 10^{-12}$ & $10.47$ & $11.86$\\

@@

For the sake of comparison we also build equilibrium sequences of magnetized disks around four Kerr BHs of varying spins, from $a=0$ to $a=0.9999$. Our numerical approach can handle BH spins as large as $|a-1|=10^{-7}$ without modifying the resolution of our numerical grid. However, for higher values of the spin parameter, we would need to increase our resolution (especially the resolution along the polar angle $\theta$ for the most highly magnetized case) but such extreme cases do not add further relevant information to our discussion. Table~\ref{KBH_disk_parameters} reports a summary of the values of the main physical quantities of these disks, whose morphology is displayed in Figs.~\ref{models_Kerr} and~\ref{models_Kerr_peri}. As for the disks built around KBHsSH, the maximum values of the enthalpy, density, pressure and magnetic pressure increase with increasing $|\Delta W|$, which, in the Kerr BH case, also means with increasing values of $a$. It can be seen that both the cusp and the centre move closer to the horizon with increasing $a$. (Note that, as we mentioned before, in the Kerr case the radial location of the horizon at the equatorial plane in perimeteral coordinates is $R_{\mathrm{H}} = 2M$ irrespective of the value of the BH spin.)

@@

The comparison of the values of the physical quantities shows that, even for highly rotating Kerr BHs, the maximum values for $h$, $p$ and $p_{\mathrm{m}}$ are lower than in the KBHsSH case. This is not a surprise, as these quantities are related to the value of $|\Delta W|$. Also, as in the case of KBHsSH, we observe a higher distorsion of the shape of the disc in the near-horizon region with increasing sphericity $\mathfrak{s}$ (and spin, in this particular case). \tf{Describe further the table and the figures}. \tf{Mention that the horizon location is constant in perimeteral coordinates irrespective of $a$.} \sg{Done}

>>>>

In recent years, new families of stationary, asymptotically flat black holes (BHs) avoiding the so-called ``no hair" theorems, have been obtained both in general relativity and in modified gravity (see e.g.~\cite{Herdeiro:2015_review} and references therein). Among those, Kerr BHs with synchronised hair~\cite{Herdeiro:2014a,Herdeiro:2016} are a counterexample to the no hair conjecture resulting from minimally coupling Einstein's gravity to simple (bosonic) matter fields obeying all energy conditions. The physical conditions and stability properties of these classes of {\it hairy} BHs  (HBHs) have been recently investigated to assess their potential viability as  alternatives to astrophysical Kerr BHs.  On the one hand, Kerr BHs with Proca hair have been shown to form dynamically as the end-product of the superradiant instability~\cite{East:2017,Herdeiro:2017} (see also~\cite{Sanchis-Gual:2016,Bosch:2016} for the case of a charged scalar field around a charged BH in spherical  symmetry). On the other hand, the stability of these solutions, questioned by~\cite{Ganchev:2018} in the scalar case, has been recently revisited by~\cite{Degollado:2018} who have shown that the domain of HBH solutions for which the superradiant instability might affect their actual existence has no significance for astrophysical BHs, rendering HBHs as {\it effectively} stable.

@@

The setup considered by~\cite{Vincent:2016} in which the light source producing the BH shadow is an accretion disk, is arguably more realistic than the distant celestial sphere of~\cite{Cunha:2015}. Thick accretion disks (or tori) are common systems in astrophysics, either surrounding the supermassive central BHs of quasars and active galactic nuclei or, at  stellar scale, surrounding the compact objects in X-ray binaries, microquasars, and gamma-ray bursts (see~\cite{Abramowicz:2013} and references therein). In this paper we present new families of stationary solutions of magnetized thick accretion disks around KBHsSH that differ from those considered by~\cite{Vincent:2016}. Our procedure, which combines earlier approaches put forward by~\cite{Komissarov:2006,Qian:2009} was presented in~\cite{Gimeno-Soler:2017} for the Kerr BH case. In Ref.~\cite{Gimeno-Soler:2017} we built equilibrium sequences of accretion disks  in the test-fluid approximation endowed with a purely toroidal magnetic field, assuming a form of the angular momentum distribution that departs from the constant case considered by~\cite{Komissarov:2006} and from which the location and morphology of the equipotential surfaces can be numerically computed. Our goal in the present work is to extend this approach to KBHsSH and to assess the dependence of the morphology and properties of accretion disks on the type of BH considered, either Kerr BHs of varying spins or KBHsSH. In this first investigation we focus on disks with a constant distribution of specific angular momentum. In the  purely hydrodynamical case, such a model is commonly refereed to as a `Polish doughnut', after the seminal work by~\cite{Abramowicz:1978} (but see also~\cite{Fishbone:1976}). In a companion paper we will present the non-constant (power-law) case, whose sequences have already been computed. The dynamical (non-linear) stability of these solutions as well as the analysis of the corresponding shadows will be discussed elsewhere.

The organization of this paper is as follows: Section~\ref{framework} presents  the mathematical framework we employ to build magnetized disks in the numerically generated spacetimes of KBHsSH. Section~\ref{procedure} discusses the corresponding numerical methodology to build the disks. Sequences of equilibrium models are presented in Section~\ref{results} along with the discussion of their morphological features and properties and the comparison with models around Kerr BHs. Finally, our conclusions  are  summarized  in  Section~\ref{conclusions}. Geometrized units ($G=c=1$) are used throughout.

@@

The approach we followed in~\cite{Gimeno-Soler:2017} for the angular momentum distribution of the disks was introduced by~\cite{Qian:2009}, and it is characterized by three free parameters, $\beta$, $\gamma$, and $\eta$ (see Eq.~(7) in~\cite{Gimeno-Soler:2017}). In this work, for simplicity and to reduce the ample space of parameters of the system, we consider a constant angular momentum distribution, $l(r,\theta) = \mathrm{const}$, which corresponds to setting $\beta=\gamma=0$ in~\cite{Gimeno-Soler:2017}. This choice also allows for the presence of a cusp (and hence matter accretion onto the BH) and a centre. Following~\citep{Daigne:2004}, the specific value of the angular momentum corresponding to bound fluid elements ($-u_t<1$) is computed as the minimum of the following equation
\begin{equation}\label{eq:mb_ang_mom}
l^{\pm}_{\mathrm{b}}(r, \theta) = \frac{g_{t\phi} \pm \sqrt{ (g_{t\phi}^2-g_{tt}g_{\phi\phi})  (1+g_{tt}) } }{-g_{tt}}\,,
\end{equation}
where the plus sign solution corresponds to prograde orbits and the minus sign solution to retrograde orbits. Our convention is that the angular momentum of the BH is positive and the matter of the disk rotates in the positive (negative) direction of $\phi$ for a prograde (retrograde) disk. Equation~(\ref{eq:mb_ang_mom}) is given by~\citep{Daigne:2004} for Kerr BHs, but it is valid for any stationary and axisymmetric spacetime. For prograde motion, the function has a minimum outside the event horizon. The location of this minimum corresponds with the marginally bound orbit $r_{\mathrm{mb}}$, and the angular momentum corresponds to the Keplerian angular momentum $l_{\mathrm{mb}}$ at that point. We show the proof of this statement in Appendix~\ref{ang_mom_appendix}.

@@

To account for the magnetic field in the disks we use the procedure described by~\cite{Komissarov:2006,Montero:2007}. First, we write the equations of ideal general relativistic MHD as the following conservation laws, $\nabla_{\mu} T^{\mu\nu} = 0$, $\nabla_{\mu} \,^\ast F^{\mu\nu} = 0$, and 
$\nabla_{\mu} (\rho u^{\mu}) = 0$, 
where $\nabla_{\mu}$ is the covariant derivative and
\begin{equation}\label{eq:e-m_tensor}
T^{\mu\nu} = (\rho h + b^2)u^{\mu}u^{\nu} + (p + p_{\mathrm{m}})g^{\mu\nu} - b^{\mu}b^{\nu},
\end{equation}
is the energy-momentum tensor of a magnetized perfect fluid, with $h$, $\rho$, $p$, and $p_{\mathrm{m}}$ being the fluid specific enthalpy, density, fluid pressure, and magnetic pressure, respectively, the latter defined as $p_{\mathrm{m}} = b^2/2$. The ratio of fluid pressure to magnetic pressure defines the magnetization parameter $\beta_{\mathrm{m}} = p/p_{\mathrm{m}}$.
Moreover, $^\ast F^{\mu\nu} = b^{\mu}u^{\nu} - b^{\nu}u^{\mu}$ is the (dual of the) Faraday tensor relative to an observer with 
four-velocity $u^{\mu}$, and $b^{\mu}$ is the magnetic field in that frame, with
$b^2=b^{\mu}b_{\mu}$ (see~\cite{Anton:2006} for further details). Assuming the magnetic field is purely azimuthal, i.e.~$b^r = b^{\theta} = 0$,
and taking into account that the flow is stationary and axisymmetric, the conservation of the current density and of the Faraday tensor follow. Contracting the divergence of Eq.~\eqref{eq:e-m_tensor} with the projection tensor $h^{\alpha}_{\,\,\beta} = \delta^{\alpha}_{\,\,\beta} + u^{\alpha}u_{\beta}$, we arrive at
\begin{equation}
(\rho h + b^2)u_{\nu}\partial_i u^{\nu} + \partial_i\left(p + \frac{b^2}{2}\right) - b_{\nu}\partial_i b^{\nu}=0\,,
\end{equation}
where $i = r, \theta$. This equation can be rewritten in terms of the specific angular momentum $l$ and of the angular velocity $\Omega$, 
\begin{equation}\label{eq:diff_ver}
\partial_i(\ln |u_t|) - \frac{\Omega \partial_i l}{1-l\Omega} + \frac{\partial_i p}{\rho h} + \frac{\partial_i(\mathcal{L}b^2)}{2\mathcal{L}\rho h} = 0\,,
\end{equation}
where $\mathcal{L} = g_{t\phi}^2 - g_{tt}g_{\phi\phi}$.

@@

\begin{figure*}
\centering
\includegraphics[scale=0.37]{figures/radial_log_rho_model_I.pdf}
\hspace{-0.6cm}
\includegraphics[scale=0.37]{figures/radial_log_rho_model_IV.pdf}
\hspace{-0.6cm}
\includegraphics[scale=0.37]{figures/radial_log_rho_model_VII.pdf}
\hspace{-0.6cm}
\\
\hspace{-0.6cm}
\includegraphics[scale=0.37]{figures/log_radial_log_rho_I_ADM.pdf}
\hspace{-0.6cm}
\includegraphics[scale=0.37]{figures/log_radial_log_rho_IV_ADM.pdf}
\hspace{-0.6cm}
\includegraphics[scale=0.37]{figures/log_radial_log_rho_VII_ADM.pdf}
\hspace{-0.6cm}
\caption{Size of the disks. Top panel: Effects of the magnetization on the radial profiles of the logarithm of the density at the equatorial plane for different KBHsSH models. From left to right we show model I, IV, and VII, respectively. Bottom panel: same as the top panel but for Kerr BHs. From left to right the cases shown have the same ADM quantities as the KBHsSH model I, IV, and VII, respectively, shown in the top panel. Note that the scale shown in the horizontal axes is different in all plots.}
\label{radial_profiles_HBH}
\end{figure*}

@@

Before building the models, it is important to note that we need a sufficiently fine numerical grid to fully capture the behaviour of the physical magnitudes at the innermost regions of the disk. For this reason, we use a non-uniform $(r, \theta)$ grid with a typical domain given by $[r_{\mathrm{H}}, 199.2] \times [0, \pi/2]$ and a typical number of points $N_r \times N_{\theta} = 2500 \times 300$. Those numbers are only representative as the actual numbers depend on the horizon radius $r_{\mathrm{H}}$ and on the specific model. The spacetime metric data on this grid is interpolated from the original data obtained by~\cite{Herdeiro:2015b}. The original grid in~\cite{Herdeiro:2015b} is a uniform ($x$, $\theta$) grid (where $x$ is a compactified radial coordinate) with a domain $[0, 1] \times [0, \pi/2]$ and a number of points of $N_x \times N_{\theta} = 251 \times 30$~\footnote{Some samples are presented in~\cite{grav_web}}. To obtain our grid, we use the coordinate transformation provided in~\cite{grav_web} and interpolate the initial grid using cubic splines interpolation. An example of our grid is shown in Fig.~XXX. \tf{We will include this figure if it could be done and were meaningful.}

@@

We start presenting the morphological distribution of the models in the ($r\sin\theta, r\cos\theta$) plane in figures~\ref{models_I} and~\ref{models_II}. These figures show the rest-mass density distribution for all our KBHsSH models for 3 different values of the magnetization parameter at the centre of the disks, $\beta_{\mathrm{m_c}}$, namely $10^{10}$ (unmagnetized, left column), $1$ (mildly magnetized, middle column) and $10^{-10}$ (strongly magnetized, right column).

@@

\begin{table*}[t]
\caption{Disk parameters and values of their relevant physical magnitudes for the Kerr BH case. For all models, $R_{\mathrm{in}} = R_{\mathrm{mb}}$ , $l = l_{\mathrm{mb}}$ and $M_{\mathrm{BH}} = 1$. The meaning of the quantities reported is as in Table~\ref{HBH_disk_parameters}.}        
\label{KBH_disk_parameters}      
\centering          
\begin{tabular}{c c c c c c  c c c c c c c}
\hline\hline       
 $a$ & $\mathfrak{s}$ &  $l$ & $W_{\mathrm{c}}$ & $R_{\mathrm{in}}$ & $R_{\mathrm{c}}$ &  $\beta_{\mathrm{m_{\mathrm{c}}}}$ & $h_{\mathrm{max}}$ & $\rho_{\mathrm{max}}$ & $p_{\mathrm{max}}$ & $p_{\mathrm{m, max}}$ & $R_{\mathrm{max}}$ & $R_{\mathrm{m, max}}$\\ 
\hline           
$0$ & $1$ & $4.00$ & $-4.32 \times 10^{-2}$ & $4.00$ & $10.47$ & $10^{10}$ & $1.04$ & $1.00$ & $1.10 \times 10^{-2}$ & $1.15 \times 10^{-12}$ & $10.47$ & $11.86$\\

@@

For the sake of comparison we also build equilibrium sequences of magnetized disks around four Kerr BHs of varying spins, from $a=0$ to $a=0.9999$. These models are more general than the corresponding ones presented in~\cite{Gimeno-Soler:2017} as the $h=1$ assumption is now relaxed. Our numerical approach can handle BH spins as large as $|a-1|=10^{-7}$ without modifying the resolution of our numerical grid. However, for higher values of the spin parameter, we would need to increase our resolution (especially the resolution along the polar angle $\theta$ for the most highly magnetized case) but such extreme cases do not add further relevant information to our discussion. Table~\ref{KBH_disk_parameters} reports a summary of the values of the main physical quantities of these disks, whose morphology is displayed in Figs.~\ref{models_Kerr} and~\ref{models_Kerr_peri}. As for the disks built around KBHsSH, the maximum values of the enthalpy, density, pressure and magnetic pressure increase with increasing $|\Delta W|$, which, in the Kerr BH case, also means with increasing values of $a$. It can be seen that both the cusp and the centre move closer to the horizon with increasing $a$. (Note that, as we mentioned before, in the Kerr case the radial location of the horizon at the equatorial plane in perimeteral coordinates is $R_{\mathrm{H}} = 2M$ irrespective of the value of the BH spin.)

The comparison of the values of the physical quantities shows that, even for highly rotating Kerr BHs, the maximum values for $h$, $p$ and $p_{\mathrm{m}}$ are lower than in the KBHsSH case. This is not a surprise, as these quantities are related to the value of $|\Delta W|$. Also, as in the case of KBHsSH, we observe a higher distortion of the shape of the disc in the near-horizon region with increasing sphericity $\mathfrak{s}$ (and spin, in this particular case). This is particularly noticeable when plotting the disk morphology in terms of the perimeteral coordinates (cf.~Fig.~\ref{models_Kerr_peri}). For the $a=0.9999$ model the disk is extremely skewed and attached to the BH horizon, particularly in the highly magnetized case in which the values reported in Table~\ref{KBH_disk_parameters} for $R_{\rm in}$ and $R_{\rm c}$ are very close to each other. The appearance of the solution is more disk-like when displayed in terms of the $r$ coordinate, as shown in Fig.~\ref{models_Kerr}.

@@
